---
title: 'Statistical Inference Course Project: Part 1'
author: "Steven Durham"
date: "January 24, 2015"
output: pdf_document
---

###Overview
In this project we will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. We will set lambda = 0.2 for all of the simulations, and will investigate the distribution of averages of 40 exponentials over 1000 simulations.

```{r}
set.seed(7)
lambda <- 0.2
n <- 40
sims <- 1000
exp_sims <- replicate(sims, rexp(n, lambda))
exp_means <- apply(exp_sims, 2, mean)
```

###1. Show the sample mean and compare it to the theoretical mean of the distribution.

**Sample mean:**
```{r}
mean(exp_means)
```

**Theoretical mean:**
```{r}
1/lambda
```

```{r echo = FALSE}
hist(exp_means, xlab = "Mean", main = "Distribution of Averages of 40 Exponentials")
abline(v = mean(exp_means), col = "orange")
abline(v = 1/lambda, col = "blue")
legend("topright", c("Sample Mean","Theoretical Mean"), col = c("orange", "blue"), lwd = 1)
```

_The center of the distribution of the sample is close to the theoretical center of the distribution, as illustrated in the above figure._

***

###2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

**Sample Variance:**
```{r}
var(exp_means)
```

**Theoretical Variance:**
```{r}
((1/lambda)*(1/sqrt(n)))^2
```

_The sample variance differs in value from the theoretical variance by only:_

```{r echo = FALSE}
(((1/lambda)*(1/sqrt(n)))^2) - var(exp_means)
```

***

###3. Show that the distribution is approximately normal.

```{r}
qqnorm(exp_means)
qqline(exp_means, col = 2)
```

_Since the points in the above figure adhere pretty closely to the straight line, the distribution is said to be approximately normal._
