---
title: "Course Project Part 2"
author: "Steven Durham"
date: "January 25, 2015"
output: pdf_document
---

##Overview
In the second portion of this project, we're going to analyze the ToothGrowth data in the R datasets package. The response is the length of teeth in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

###Load the ToothGrowth data, provide a basic summary of the data, and perform some basic exploratory data analyses

```{r}
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
summary(ToothGrowth)
```

The following figure infers that at 0.5 mg and 1.0 mg, orange juice leads to increased tooth growth vs. ascorbic acid, while that advantage appears to subside with a dose of 2.0 mg.

```{r, echo=FALSE}
boxplot(len ~ supp * dose, ToothGrowth, col="red", ylab="Tooth Length", xlab="Supplement & Dose in Mg", main="Boxplots by Supplement and Dose")
```

****

###Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

_With a dose of 0.5 mg_
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose==0.5,])
```

_With a dose of 1.0 mg_
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose==1.0,])
```

_With a dose of 2.0 mg_
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose==2.0,])
```

****

###Conclusion
With a dose of 0.5 mg or 1.0 mg, the p-value is less than 0.05 and the confidence interval does not contain 0, indicating that at those doses, orange juice leads to increased tooth growth vs. ascorbic acid. However, with a dose of 2.0 mg, the p-value is greater than 0.05 and the confidence interval contains 0, indicating that there isn't a significant difference between orange juice and ascorbic acid at that dose.